### 2017-08-15 2017mergingmerges/section/XX-Related.tex
filter fusion supports straight line computations, no splits or joins
Copy edits to related work

Filter Fusion~\cite{proebsting1996filter} uses a similar algorithm, but only supports processes with at most one input and one output channel.
Each output channel may only be used once.
This means combinators such as @zip@, @unzip@, @append@, and @partition@ cannot be expressed.
Here a consumer and a producer are fused by alternating between the two; when the consumer needs input, control is passed to the producer, and when the producer has output, control is passed to the consumer.
This is sufficient when only one channel is shared, but when multiple channels are shared finer-grained coordination is required.

>>>>

Like our own Machine Fusion,  Filter Fusion~\cite{proebsting1996filter} also statically interleaves the code of producer and consumer processes. Each process must have a single input and output channel, so common operators like @zip@, @unzip@, @append@, @partition@ and so on are not supported. Given an adjacent producer and consumer pair, Filter Fusion alternately assigns control to the code of each. When the consumer needs input control is passed to the producer, and when the producer produces its value control is passed back to the consumer. This simple scheduling algorithm works only for straight line pipelines of processes. Machine fusion provides a finer grained interleaving of code, which is nessesary to support branching dataflows that contain both splits and joins.

%Filter Fusion~\cite{proebsting1996filter} uses a similar algorithm, but only supports processes with at most one input and one output channel.
% This means combinators such as @zip@, @unzip@, @append@, and @partition@ cannot be expressed.
%Also, the process network must be a straight line, with no splits or joins.
%Here a consumer and a producer are fused by alternating between the two; when the consumer needs input, control is passed to the producer, and when the producer has output, control is passed to the consumer.
%This is sufficient when only one channel is shared, but when multiple channels are shared finer-grained coordination is required.
